Lawrence Bull, PhD

### 2023-01-16 index.qmd
edit index, writing

I'm particularly interested in _multilevel structures_ that appear in measurements from populations of systems -- trains, [planes](), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (... [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise in a Bayesian workflow, complex models can be built from interpretable units, allowing machines to share information and increase the value of data.
At the population level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts.

>>>>

I'm particularly interested in _multilevel structures_ that appear in measurements from populations of systems -- trains, [planes](), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (... [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise in a Bayesian workflow, complex models can be built from interpretable units, allowing machines to share information and increasing the value of data.
At the population level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts.

### 2023-01-16 writing.qmd
edit index, writing

### [Introduction to Engineering Pattern Recognition](https://github.com/labull/EPR-lectures)
Guest Lectures for the Advanced Dynamics course at the University of Sheffield in the Engineering dept.
A light introduction to machine learning in the context of some engineering examples:

>>>>

### [Introduction to Engineering Pattern Recognition](https://github.com/labull/EPR-lectures)
Guest Lectures for the Advanced Dynamics [MEC452] undergraduate course at the University of Sheffield in the Engineering Dept.
A light introduction to machine learning in the context of some engineering examples:
